Face Attractiveness and the Sense of Reality

### 2022-08-29 analysis.Rmd
format duration

```{r message=FALSE, warning=FALSE}
dfsub <- df |>
  group_by(Participant) |>
  select(Participant, starts_with("Attention")) |>
  slice(1) |>
  ungroup() |>
  mutate(Attention_Check = mean(c(Attention_Check1, Attention_Check2, Attention_Check3))) |>
  arrange(Attention_Check)
```

@@

```{r message=FALSE, warning=FALSE}

```

@@

```{r message=FALSE, warning=FALSE}
data.frame(Participant = c("Total"), t(sapply(dfsub[2:ncol(dfsub)], mean, na.rm = TRUE))) |>
  rbind(dfsub) |>
  knitr::kable() |>
  kableExtra::row_spec(1, italic = TRUE) |>
  kableExtra::row_spec(which(dfsub$Participant %in% outliers) + 1, background = "#EF9A9A")
```

>>>>

```{r message=FALSE, warning=FALSE}
dfsub <- df |>
  group_by(Participant) |>
  select(Participant, starts_with("Attention"), starts_with("Duration")) |>
  slice(1) |>
  ungroup() |>
  rowwise() |> 
  mutate(Attention_Check = mean(c(Attention_Check1, Attention_Check2, Attention_Check3))) |> 
  ungroup() |> 
  arrange(Attention_Check)
```

@@

```{r message=FALSE, warning=FALSE}
df 
```

@@

```{r message=FALSE, warning=FALSE}
data.frame(Participant = c("Total"), t(sapply(dfsub[2:ncol(dfsub)], mean, na.rm = TRUE))) |>
  rbind(dfsub) |>
  mutate(Attention_Check = paste0(
    insight::format_value(Attention_Check, 1), 
    " (", insight::format_value(Attention_Check1, 0), 
    ", ",
    insight::format_value(Attention_Check2, 0), 
    ", ",
    insight::format_value(Attention_Check3, 0),
    ")")) |> 
  select(-Attention_Check1, -Attention_Check2, -Attention_Check3) |> 
  datawizard::data_relocate("Attention_Check", 2) |> 
  knitr::kable() |>
  kableExtra::row_spec(1, italic = TRUE) |>
  kableExtra::row_spec(which(dfsub$Participant %in% outliers) + 1, background = "#EF9A9A")
```
